%Cite and summarize here relevant and significant literature (dissertations, theses, journals, patents, notable conference papers) to prove that no one has done your work yet. 

There are several existing studies or researches about different kinds of applications of air parameters. Most of the studies found relating to these parameters are temperature, humidity, temporal, wireless air quality and discomfort index monitoring systems and air quality standards.

\section{Temperature Monitoring System}
%Temperature is the degree of hotness or coldness of an object or a substance.

%cite Wireless Monitoring of Soil Moisture, Temperature & Humidity Using Zigbee in Agriculture
An important parameter, not only in the air but also in everything, is the temperature, according to \cite{Chavan}. It is very important to monitor temperature of objects because most objects are sensitive to changes in the temperature such as products and some machines. Some existing researches of temperature monitoring system are found in the field of agriculture. Recent studies~\cite{Chavan} shows how important data-acquisition systems in the agriculture through environmental monitoring. Environmental monitoring refers to the gathering of data of some parameters in the environment that may affect the products. Automated measurements are beneficial because gathering of data and measurements are made several times. Chavan and Karande have developed a system for wireless monitoring of soil moisture, temperature and humidity in the field of agriculture. The system uses a temperature sensor, humidity sensor and soil moisture sensor that are connected to an AVR microcontroller. It also uses GSM-Zigbee based remote monitoring and control system. The application of Zigbee to the monitoring system in the agriculture reduces human power and enables to evaluate some accurate changes that will happen. 

%cite Smart Home Automated Control System Using Android Application and Microcontroller
Aside from the agricultural implementation of temperature monitoring, there are also existing studies that involves its application to automated systems for electronic devices or appliances.
~\cite{Mohamed} designed a smart home automated control system. The system uses a microcontroller for sensors and android application for the transmission of data and the receiving of data. One of the four major fields of the smart home system or SHS is the environmental monitoring, which includes the monitoring of the humidity and the temperature. The main components used in the system are microcontroller, adruino board, android and a bluetooth module. Wireless internet services are also used for several monitoring and controlling processes. The passive infrared sensors are capable off detecing movements of a human being through sensing the changes in the temperature over the scene. The SHS also uses LM35 temperature sensor for the Temperature sensing system for Air Conditioner. The system can transfer data from the sensors to the android phone. On the same way, it can transmit data or commands from the android to the appliances. The wireless monitoring of temperature allows the user to control electronic devices or appliances from anywhere in the world.

%cite A low-cost microcontroller-based system to monitor crop temperature and water status
%Fisher and Kebede have designed and developed a microcontroller-based system to monitor the temperature and the water status of crops. They use an infrared thermometer, TC74 digital temperature sensor, LM35 analog temperature sensor and a Watermark sensor to obtain data about the canopy, soil and air temperature measurements and the status of the soil's moisture respectively. The microcontroller will enable the sensors to read 10 times and are automatically averaged. The data are collected with an interval of an hour and are stored in the memory chip. The microcontroller-based system developed is designed mainly for automated monitoring of the conditions of the crops.

%cite A Microcontroller- based Room Temperature
%A research was made on how important monitoring of the temperature of a computer server room may affect the performance of the server. Computer servers are the backbones that supports the computer network of the organization and the task that are IT-related and therefore, temperature monitoring is very essential. These researchers designed a microcontroller-based room temperature monitoring system for maintaining the performance of the computer servers. They use Atmel ATmega8535 microcontroller and LM35 temperature sensor as the main component of the system. The system also includes a GSM modem and a relay board that will send a short message service or SMS to the server administrator and can control electronic devices through SMS sent by the administrator respectively.  

\section{Humidity Monitoring System}
%It is the measurement of moisture or water vapor that are present in the air. 
Humidity is always associated with temperature. It plays an important role to human due to the skin being sensitive to the changes in humidity. This is also the reason why humans sweat. Not only humans are affected by the changes in the humidity in the air but also applies to the things related to the field of agriculture. 

%Green House Monitoring and Controlling Using Android Mobile Application
A group of researchers~\cite{Aji} designed a green house monitoring and controlling system using an android mobile application. The system can control the humidity inside a green house, based on the readings of the humidity sensor through the microcontroller which is connected to the central server and can be accessed through Wi-Fi connection. The system is consists of humidity sensor, Arduino UNO microcontroller, serial communication, wireless connection and a computer. The data from the sensor will be transmitted to the microcontroller and transferred to the computer through serial communication. The computer will transmit the data to the android phone via wireless connection and the android phone can now control the system depending on the commands that will be selected. The android can receive data from the humidity sensor, send data for water sprayer to turn on, send data for stepper motor to work and other commands that the system is capable of doing. This system ensures the condition of the green house environment to be in good condition.

%cite A Low-Power Wireless Sensor for Online Ambient Monitoring
Other than agricultural applications, studies also shows how air quality such as temperature and humidity affects the health of a human being. Indoor air quality or IAQ is an important factor that may affect the level of comfort and the health of the people. This may increase the discomfort index of a human being which may result to difficulties in concentration or even headaches.~\cite{Folea} develop a wireless battery-powered system for online ambient monitoring. The system has the ability to monitor temperature, humidity, carbon dioxide level, absolute pressure and intensity of light in the indoor spaces. The data gathered can be sent through a computer for visualization and can send SMS for alarms. The system has sensors such as ambient, temperature, humidity and many more sensors to evaluate the indoor air quality. Wi-Fi connection is used as a data transmission, from the sensors to the computer, due to the fact that Wi-Fi can be found in almost every home. The study of indoor air quality will help prevent or solve issues that may affect the health and the performance of the people.

%cite Development of a grain monitoring probe to measure temperature, relative humidity, carbon dioxide levels and logistical information during handling and transportation of soybean
%Danao, Zandadoni and Gates developed a probe that can monitor and measure temperature and relative humidity during the transportation of soybeans and stated that humidity levels remained relatively uniform during the transportation of products. Products such as soybeans have a specific measurement of humidity or the moisture content in order to maintain its qualities. It just shows that humidity is a big factor for the preservation of products in the agriculture. Thus, measuring and maintaining the humidity of the products and the changes to the surroundings is very important.

\section{PM$_{10}$ Temporal Monitoring}

PM$_{10}$ or particulate matter that have a diameter of 10 micrometers wide which are classified under fine particles. One study~\cite{Wong} used an internet protocol camera to observe real time changes in the amount of particles found in the air. The camera points to a reference location and the still images were divided into the RGB bands.

They developed an algorithm which makes use of the atmospheric reflectance and the concentration of the PM$_{10}$ using regression. The amount of reflectance is measured using a spectroradiometer and the concentration of the particles are determined by the different RGB bands of the camera. The PM$_{10}$ and the atmospheric reflectance are found to be linearly related through using the skylight parameter model, which utilizes the sun's radiation. The results produced were compared to a DustTrak meter and provide a high correlation coefficient of .78. 

\section{Wireless Air Quality Monitoring System}

A study~\cite{Reilly} monitored the amount of different air pollutants using Arduino. The pollutants that are measured are carbon monoxide, PM$_{2.5}$, and ozone which make use of the MQ-7 sensor, MQ-131 sensor, and Sharp dust sensor respectively. The sensors are mounted onto a redboard as well as GSM shield to send data wirelessly. The sensors are calibrated using a co-located ADEQ (Air Quality Division) sensor and were validated. The device is placed around the metro area and the data collected will be compared to a monitoring station.  Data was collected for a period of time and a trend was found in CO and ozone levels. However, the use of the Sharp dust sensor was not very effective but could find slight differences at high pollution times with low pollution times.

Another similar study~\cite{Hebbar} of an air monitoring device is implemented using a microcontroller where several sensors are placed and data is sent through GSM wirelessly. The design tests the amount of CO$_{2}$ levels indoors. It also measures the temperature and humidity of the atmosphere locally. Calibration of the sensors is done by concentrating known amount of a certain gas into a test chamber and determine its offset from the results obtained. The design was tested in a seminar hall and the results obtained showed that the start and end of each class attributed to the increase in CO$_{2}$ emission. The design also shows the data through an online GUI.

One similar design, called HazeWatch, is done using several sensors and cloud computing~\cite{Hu}. The design is made compact and portable and can be mounted onto a car or bike.  Data is harvested using a mobile phone and records the location in real time. Data is then sent wirelessly to cloud-based servers and is interpolated (Inverse Weighing and Ordinary Kriging interpolation) to generate estimates. The data can then be view visually using contour maps of the pollution or gas concentration levels in the area. The results obtained are compared to similar products (\textit{Node} and \textit{SensorDrone})

\section{Discomfort Index Monitoring System}

%cite Design of a Room Monitoring System for Wireless Sensor Networks
A research was made about the importance of monitoring and controlling of atmospheric conditions to the efficiency of the performance of the human beings ~\cite{Sun} . They designed a wireless sensor module that uses a Zigbee communication and sensor module, which consists of temperature, humidity, CO$_{2}$ and atmospheric pressure sensor, that maintains a comfortable environment for human beings or to prevent discomfort. The sensor module is the transmitter which delivers the sensor data to the receiver and the receiver will transmit the filtered or recovered sensor data to a microcontroller board in monitoring the room environment. The room monitoring system is able to provide a comfortable environment for human beings through the wireless sensor network or WSN for monitoring the room environment.

\section{Air Quality Standards}

This review shows the different indoor air quality standards set by different countries across the world. The data is collected from documents from different health and environmental organization. This paper can be set as a tool for evaluating acceptable concentrations of different pollutants within an area. The pollutants included in this study are "carbon dioxide (CO$_{2}$), carbon monoxide (CO), formaldehyde (HCHO), nitrogen dioxide (NO$_{2}$), sulfur dioxide (SO$_{2}$), total volatile organic compounds (TVOCs) and particulate matter (PM$_{2.5}$ and PM$_{10}$)." The amount allowable depends on how bad the amount of a certain pollutant exists indoors. The paper also explains different harmful health effects each pollutant has on the human body.
 
%\section{Summary}
  






